--- 
title: "SOP manual for fMRI analysis: Part 1"
author: "Christian Coffman"
date: 2020-10-22 # "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a series of SOP files of using the facilities to start your research in the Division of Biostatistics in SPH@UMN, esp. focusing on fMRI image analysis."


---
This is a series of SOP files of using the facilities to start your research in the Division of Biostatistics in SPHatUMN, esp. focusing on fMRI image analysis.

# Prerequisites

This is a _sample_ book written in **Markdown**. 

This is a series of SOP files of using the facilities to start your research in the Division of Biostatistics in SPHatUMN, esp. focusing on fMRI image analysis.

You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
# install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
